\documentclass[a4paper,9pt]{extarticle}
% -----------------------------------------------------------
\usepackage[top=0.55in, left=0.45in, right=0.75in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage[super]{nth}
\usepackage{palatino}
\usepackage{tabularx}
\usepackage{hyperref}
\fontfamily{SansSerif}
\selectfont
\usepackage[T1]{fontenc}
\usepackage
% [ansinew]
[utf8]
{inputenc}
\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=10in
\raggedbottom
%\def\labelitemi{\scriptsize$\blacksquare$}

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemiii}{$\circ$}

\pagestyle{empty}
% -----------------------------------------------------------
% Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
  \begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
    \textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
  \end{tabular*}\vspace{-8pt}}
% -----------------------------------------------------------

\begin{document}
%\renewcommand{\labelitemii}{$\blacksquare$}
\hspace{0.5cm}\\[-0.2cm]
% \vspace{-5mm}
{\huge Nishant Gupta}\vspace{-1mm} \hrule \vspace{2mm}
\indent Final Year Student,  \hfill \textit{Github/Bitbucket} : \texttt{Nishant9}  \\
\indent Computer Science and Engineering, \hfill Email-id : \textit{nishgu@iitk.ac.in}  \\
\indent IIT Kanpur \hfill Mobile No.: \textit{7275726006} \\
\vspace{-1mm}
\hspace{5mm}\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\ \vspace{-2mm}
% \begin{table}[ht!]
\begin{center}
  
  \indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l }
            \textbf{Year}  & \textbf{Degree} & \textbf{Institute} & \textbf{CPI/\%} \\
            2017 (expected) & {Bachelor of Technology} & IIT Kanpur  & 9.4/10.0  \\ 
            2013 & {HSCE} & Shivpuri Public School,Ashoknagar & 			93.60\%	\\
            2011 & AISSCE & Tara Sadan School,Ashoknagar  & 9.6/10.0   \\
          \end{tabular}
        \end{center}

        \vspace{-1mm}\resheading{\textbf{SCHOLASTIC ACHIEVEMENTS} }\\[\lsep]
        \vspace{1mm}        
        \begin{itemize} \itemsep -2pt
        \item Awarded \textbf{Academic Excellence Award} (IITK) given to top 5\% students on the basis of academic performance.
        \item Secured \textbf{AIR-248} out of 0.15 million shortlisted  students in JEE-Advanced 2013.
        \item Qualified \textbf{Regional Mathematical Olympiad}(Rajasthan
          Region) that selects only 40 students from Rajasthan.
        \item Selected for the \textbf{KVPY} (Kishore Vaigyanik Protsahan Yojana) in 2013.
        \end{itemize}

        \resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
        \vspace{1mm}
        \begin{itemize} \itemsep -3pt
        \item \noindent \textbf{Languages :} C/C++, Python, R, Haskell,
          Javascript, Scala, x86 Assembly, Perl
        \item \noindent \textbf{Operating Systems :} Linux(Gentoo, ArchLinux,
          NixOS), Windows
        \item\textbf{Frameworks/Libraries :} django, OpenCV, Parsec,
          data.table, dplyr, ggglot, cabal, Angular, spark
        \item\textbf{Softwares :} Emacs, Vim, AndroidStudio, IntelliJ Idea,
          RStudio
        \item\textbf{Others :} git, svn, ElasticSearch, \LaTeX, css/scss, SQL, HTML, Bash
        \end{itemize}

        \resheading{\textbf{AREAS OF INTEREST} }\\[\lsep]
        \vspace{3mm}\\
        \indent Functional Programming, Machine Learning, Computer Networks, Operating
        Systems, Graph Theory, \\
        \indent Optimisation, Algorithms, Theory of Computation
        \vspace{1mm}
        
        \resheading{\textbf{PROFESSIONAL EXPERIENCE} }\\[\lsep]
        \vspace{1.2mm}\begin{itemize} \itemsep -2pt
        \item \textbf{Goldman Sachs}( Summer Employee) \hfill
          \textit{May'16-Jul'16(10 weeks)}
          \vspace{-2mm}\begin{itemize} \itemsep -1pt
          \item \textbf{Job Failure analytics}
          \vspace{-1.2mm}\begin{itemize} \itemsep -1pt
            \item Improvised Job Failure prediction model and automated the
              crucial task of structured analytics.
            \item Proposed and tested root cause detection model which leverages
              micro and macro failure patterns to detect probable failure causes
              and sends recommendation to concerned teams.
            \end{itemize}
          \item \textbf{ETA and SLA Breach prediction model}
          \vspace{-1mm}\begin{itemize} \itemsep -2pt
            \item Transformed ETA and SLA prediction model to account for more
              complex dependencies.
            \item Fabricated and partially implemented a dynamic model which
              \begin{itemize}
              \item Can dynamically incorporate Job failure model to alter the
                prediction.
              \item Changes prediction throughout the day in reaction to various
                jobs and telemetries.
              \item In manual testing, exhibited twice the recall and a slight
                increase in precision
              \end{itemize}
            \end{itemize}
          \item Rewrote the entire data ingestion pipeline for both models which now
            accounts for 90 percent of jobs compared to 60 percent in earlier
            pipeline and with 40 percent more efficiency.
          \end{itemize}
        \item \textbf{  Altisource Business Solutions}( Technology Intern) \hfill
          \textit{May'15-Jul'15(8 weeks)}
          \vspace{-2mm}\begin{itemize} \itemsep -2pt
          \item Worked on the projects \textbf{Actor Equivalence and Identity Stitching} and \textbf{Event Data Clustering} for the company's consumer analytics product `Pointilist'
          \item Designed an algorithm for solving the actor equivalence problem (Established a relation between actors and streaming events) for single Multiple platforms.
          \item Built a generic framework that takes varying Consumer data from different tenants and Processes, normalizes and Clusters it to derive meaningful inferences.
          \end{itemize}
        \end{itemize}

        \vspace{-1mm}\resheading{\textbf{WORK EXPERIENCE} }\\[\lsep]\vspace{1mm}
        \begin{itemize} \itemsep -1mm 
        \item \textbf{Hscraper} - \textit{github:}
          \href{http://www.github.com/Nishant9/Hscraper}{\texttt{Nishant9/Hscraper}}, 
          \textit{hackage:}
          \href{https://hackage.haskell.org/package/hScraper}{\texttt{Hscraper}}
          \\ - \textit{Mentor: Prof. Piyush P Kuroor} \hfill \textit{Aug'15-Dec'16}
          \vspace{-2mm}\begin{itemize} \itemsep -2pt
          \item \textbf{Haskell} library to scrape and crawl webpages.
          \item Includes an HTML Parser and a
            basic query language parser, both written using \textbf{Parsec}. 
          \item Query language supports contiguous filters with optional
            attribute matching.
          \item HTML Parser parses correct HTML by itself and has tidyhtml
            bindings to correct malformed html.
          \item Includes a Network module that is a wrapper around
            \textbf{http-conduit} to allow for bulk requests with varying
            parameters and responses.
          \item Current maintainer of library on hackage.
          \end{itemize}
          \newpage
        \item \textbf{Object detection and Multiclass classification of Video
            Surveillance feed} \\ - \textit{Mentor: Prof. Harish Karnick} \hfill \textit{Jan'16-Apr'16}
          \vspace{-2mm}\begin{itemize} \itemsep -2pt
          \item Achieved greater than 95 percent accuracy and precision  using
            Convolutional neural networks for feature extraction and SVM for classification 
          \item Used VGG-16 caffe model and python implementation of Faster R-CNN paper published in
            NIPS 2015
          \item Takes around 1sec/frame on a laptop GPU(Nvidia GTX-755M)
          \item Also Tried various combinations of tradional approaches for
            feature extraction from images.
            Some of them are :
            \begin{itemize}
          \item Mixture of Gaussians from OpenCV for ROI extraction and own
            implementation of Non-maximum Suppression for refinement of ROI
          \item Experimented with different feature representations of ROI like
            HSV, HoG and SIFT for training the classifiers.
          \item Achieved greater than 85 percent accuracy and greater than 80
            percent precision using Linear SVM as classifier and HoG feature
            representation with other refinements.
            \end{itemize}
          \end{itemize}
          
        \item \textbf{Scala Complier} - \textit{github:}
          \href{http://www.github.com/Nishant9/scalaCompiler}{\texttt{Nishant9/scalaCompiler}}
          \\ - \textit{Mentor: Prof. Subhajit Roy} \hfill \textit{Jan'16-Apr'16}
          \vspace{-2mm}\begin{itemize} \itemsep -2pt
          \item Implemented Scala to X86(AT\&T Syntax) in python using
            ply(Python lex yacc)
          \item Supports basic data types, loops, switch statements,
            conditionals, n dimensional arrays, nested functions, recursion
          \item Implements dynamic scoping, type checking and basic type inference  
          \end{itemize}
          
        \item \textbf{Code Cloud} - \textit{github:} \href{http://www.github.com/Nishant9/ccloud}{\texttt{Nishant9/ccloud}} 
          \\ - \textit{Mentor: Prof. Sumit Ganguly} \hfill \textit{Jan'16-Apr'16}
          \vspace{-2mm}\begin{itemize} \itemsep -2pt
          \item Code management website mainly focused on Competitve programming
          \item Uses django for backend, bootstrap3 for frontend and sqlite for database
          \item Allows public and private code sharing, is fully mobile
            compliant, implements basic search functionality.  
          \end{itemize}
          
        \item \textbf{NachOS extension} - \textit{Under Prof. Mainak Chaudhari} \hfill \textit{Aug'15-Dec'15}
          \vspace{-2mm}\begin{itemize} \itemsep -2pt
          \item  Implemented system calls pertaining to Fork, Exec, Join, Yield, Sleep and Exit for NachOS (a rudimentary OS)
          \item Programmed different signal handling methods, process scheduling and page replacement algorithms and evaluated
            their relative performance
          \item Implemented and tested various synchronization primitives like
            mutex and semaphores
          \end{itemize}
        \item \textbf{Online Web Platform} - \textit{Under Prof. Manindra Agarwal} \hfill \textit{Nov'14-Present}
          \vspace{-2mm}\begin{itemize} \itemsep -2pt
          \item Implemented Google Drive Integration and various small features for a web platform that uses \textbf{Dart} on front-end and \textbf{Scala} on back-end. 
          \item Designed and developed the frontend using bleeding edge frameworks like \textbf{AngularDart}, Polymer, etc 
          \item Currently developing Android app for same web platform.
          \end{itemize}
        \item  \textbf{Sentiment Analysis of Social Media} - \textit{Takneek'14 }   \hfill \textit{ Aug'14}          
          \vspace{-2mm}\begin{itemize} \itemsep -2pt
          \item Application developed during Web-Dev, Takneek'14 and secured \textbf{\nth{1}} position.
          \item Provided an interface to analyse the past and present social sentiment of brands and their products.
          \item  Identify `good' and `bad' features of the product and suggest weak points to improve it.
          \end{itemize}
        \item
          \textbf{Triangulation of Image} - \textit{ Programming Club, IIT Kanpur }                  \hfill \textit{Jun'14-Jul'14}
          \vspace{-2mm}\begin{itemize}  \itemsep -2pt
          \item Renders image using only triangles and gives the sense of image.
          \item Uses \textbf{OpenCV} for Image Processing and Manipulation, Tkinter for GUI and webcam support.
          \item Uses Delaunay Triangulation so that image is aesthetically pleasing.
          \end{itemize}
        \item
          \textbf{Location Extraction and Visualization of News items} - \textit{ ACA, IIT Kanpur }
          \hfill  \textit{Feb'14-Apr'14}
          \vspace{-2mm}\begin{itemize} \itemsep -2pt
          \item A webapp that plots news on a world map  using various APIs for location resolution, news fetching and map plotting.
          \end{itemize}
        \end{itemize}

        \resheading{\textbf{RELEVANT COURSEWORK} }\\[\lsep] \vspace{2mm}
        \begin{itemize}
        \item[]
          \begin{tabular}{p{69mm}@{\hskip 0.25in} p{80mm}} 
            CS330 - Operating Systems(\textbf{A*}) & CS340 - Theory of Computation(\textbf{A*})  \\
            CS345 - Algorithms II(\textbf{A}) & CS335 - Compiler Design(\textbf{A})  \\
            CS653 - Functional Programming(\textbf{A}) & CS771 - Machine learning(\textbf{A})  \\
            CS252 - Computing Laboratory - II(\textbf{A*}) & CS251 - Computing Laboratory - I(\textbf{A})  \\
            CS210 - Data Structures and Algorithms(\textbf{A*}) & CS201 - Discrete Mathematics(\textbf{A})  \\
            CS345 - Software Engineering(\#)             & MSO201 - Probability and Statistics(\textbf{A}) \\
            CS653 - Computer Networks(\#)  & \hfill \# - Ongoing
          \end{tabular}

        \end{itemize}

        \vspace{-1mm}
        \resheading{\textbf{MISCELLANEOUS} }\\[\lsep] \vspace{1mm}
        \begin{itemize} \itemsep -2pt
        \item \textit{Seceretary} of Programming Club, IIT Kanpur. \hfill \textit{2014-2015}
          \vspace{-2mm}\begin{itemize}
          \item Part of a team of 15 members made to manage the activities of the Programming Club, IITK
          \item Mentored freshmen for various Programming club competitions.
          \end{itemize}
        \item \textit{Co-ordinator},
          Funzone, Udhghosh'14 - Annual Inter-College Sports Fest of IIT-Kanpur. \hfill \textit{Sep'2014}
        \end{itemize}\vspace{-\baselineskip}
      \end{document}

