%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
% 
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
% 
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com)
% 
% License:
% The MIT License (see included LICENSE file)
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

% ----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
% ----------------------------------------------------------------------------------------

\documentclass[a4paper]{twentysecondcv} % a4paper for A4
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{nth}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{helvet}


\renewcommand{\familydefault}{\sfdefault}
\setmainfont{Helvetica}
\setsansfont{Helvetica}
%----------------------------------------------------------------------------------------
% PERSONAL INFORMATION
% ----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\cvname{Nishant Gupta} % Your name
\cvjobtitle{CSE, IIT Kanpur} % Job title/career

\cvdate{} % Date of birth
\cvaddress{} % Short address/location, use \newline if more than 1 line is required

\cvnumberphone{+91 7275726006} % Phone number
\cvsite{} % Personal website
\cvmail{nishant@cse.iitk.ac.in} % Email address

\newcommand{\sbt}{\,\begin{picture}(-1,1)(-1,-3)\circle*{2.4}\end{picture}\space\ }

% ----------------------------------------------------------------------------------------

\begin{document}

% ----------------------------------------------------------------------------------------
% ABOUT ME
% ----------------------------------------------------------------------------------------

\aboutme{
  \vspace{-2mm}
  \textbf{B. Tech, CPI - 9.4/10} \hfill \textbf{May 2017} \\
  CSE, IIT Kanpur \\
  \vspace{2mm}
  \textbf{HSCE (+2), \space 93.6\%} \hfill \textbf{April 2013}\\  
  Shivpuri Public School \\
  \vspace{2mm}
  \textbf{AISSCE, 9.6/10}\hfill \textbf{April 2011} \\
  Tara Sadan School \\
}

\Achieve{
  \vspace{-2mm}
  % \subsection{Competitions}
	\begin{list3}
  \item JEE 2013 - AIR 248 out of 0.15 Million shortlists(1.3 million total)
  \item Academic Excellence Award (IITK)
  \item KVPY Scholar
  \item Qualified Regional mathematical Olympiad
  \end{list3}

}
% ----------------------------------------------------------------------------------------
% SKILLS
% ----------------------------------------------------------------------------------------

% Skill bar section, each skill must have a value between 0 an 6 (float)
\tool{
  \vspace{-2mm}
  \subsection{Languages}
  \vspace{-2mm}
  Python, C/C++, Haskell, Agda, R, Bash, Javascript, Scala, Perl, x86 Assembly
  \vspace{-2mm}
  \subsection{Frameworks/Libraries}
  \vspace{-2mm}
  django, OpenCV, Parsec,
  data.table, dplyr, gglot, cabal, Angular, spark
  \vspace{-2mm}
  \subsection{Operating Systems} 
  \vspace{-2mm}
  Linux(Gentoo, ArchLinux, NixOS)
  \vspace{-2mm}
  \subsection{Others} 
  \vspace{-2mm}
  Emacs, Vim, Git, svn, ElasticSearch, \LaTeX, css/scss, SQL, HTML, nix

}

\tutor{
  \vspace{-3mm}
  Computer Networks, Machine Learning, Compiler Design,
  Functional Programming, Databases, Programming Languages,
  Software Architecture, Operating Systems,
}


\extra{
  \vspace{-2mm}
  % \subsection{Competitions}
	\begin{itemize}[leftmargin=*]
  \item {\large Sentiment Analysis of Social Media}, \hfill Jul'14-Aug'14\\
    Won \nth{1} prize in Web-Dev, a webapp development competition in Takneek'14.
  \item {\large Secretary},\\
    Programming Club \hfill 2014-2015 
  \item {\large Coordinator},\\
    Funzone, Udhghosh'14 \hfill Aug'14 

  \end{itemize}


}

% ------------------------------------------------

% Skill text section, each skill must have a value between 0 an 6


% ----------------------------------------------------------------------------------------

\makeprofile % Print the sidebar

% ----------------------------------------------------------------------------------------
% INTERESTS
% ----------------------------------------------------------------------------------------
\vspace{-2mm}
\section{Professional Experience}
\vspace{-2mm}

\subsection{\textbf{Goldman Sachs}}
\vspace{-2mm}
Intern, Bangalore \hfill \emph{May `16-July'16(10 weeks)}\\
\vspace{-4mm}\begin{list3}
\item \textbf{Job Failure analytics}
  \begin{list3}
  \item Improvised Job Failure prediction model and automated the
    crucial task of structured analytics.
  \item Proposed and tested root cause detection model which leverages
    micro and macro failure patterns to detect probable failure causes
    and sends recommendation to concerned teams.
  \end{list3}
  \item \textbf{ETA and SLA Breach prediction model}
  \begin{list3}
  \item Transformed ETA and SLA prediction model to account for more
    complex dependencies.
  \item Designed and partially implemented a dynamic model which
    \begin{list3}
    \item Can dynamically incorporate Job failure model to alter the
      prediction.
    \item Changes prediction dynamically in reaction to various
      jobs and telemetries.
    \item In manual testing, exhibited twice the recall and a slight
      increase in precision
    \end{list3}
  \end{list3}
\item Rewrote the entire data ingestion pipeline for both models which now
  accounts for 90 percent of jobs compared to 60 percent in earlier
  pipeline and with 40 percent more efficiency.
  \newline
  \newline
\end{list3}

\subsection{ \textbf{Altisource Business Solutions} }
\vspace{-2mm}
Intern, Bangalore \hfill \emph{May `15-July'15(8 weeks)}\\
\vspace{-3mm}
\begin{list3}
\item Worked on the projects \textbf{Actor Equivalence and Identity Stitching} and \textbf{Event Data Clustering} for the company's consumer analytics product `Pointilist'
\item Designed an algorithm for solving the actor equivalence problem (Established a relation between actors and streaming events) for single Multiple platforms.
\item Built a generic framework that takes varying Consumer data from different tenants and Processes, normalizes and Clusters it to derive meaningful inferences.
  \newline
  \newline
  \newline
\end{list3} 

\vspace{-2mm}
\section{Selected Projects}
\vspace{-2mm}
\subsection{\textbf{Hscraper: A Haskell library to scrape and crawl webpages.}}
\vspace{-2mm}
\hspace{1mm}- \faGithub
\href{http://www.github.com/Nishant9/Hscraper}{\texttt{Nishant9/Hscraper}}, 
\textit{hackage:}
\href{https://hackage.haskell.org/package/hScraper}{\texttt{Hscraper(\textbf{Current maintainer})}}
\hfill
\vspace{1mm}
\begin{list3}% \itemsep -2pt
\item Developed an HTML Parser and a basic query language parser with support for contiguous filtering with optional attribute matching.
\item HTML Parser parses correct HTML by itself and has tidyhtml
  bindings to correct malformed html.
\item Includes a Network module that is a wrapper around
  \textbf{http-conduit} to allow for bulk requests with varying
  parameters and responses.
  \newline
  \newline
\end{list3}

%\vspace{-1mm}

\subsection{\textbf{Detection and Classification in Video Surveillance feed}}
\vspace{-2mm}
\hspace{1mm}- \textit{Mentor: Prof. Harish Karnick} \hfill \emph{Jan'16-Apr'16}
\vspace{1mm}
\begin{list3} 
\item Achieved greater than 95 percent accuracy and precision  using
  \textbf{Recurrent Convolutional neural networks} desribed in Faster R-CNN paper published in
  NIPS 2015
\item Also achieved greater than 85 percent precision and recall using tradional
  approaches for image processing and
  feature extraction such as Mixture Of Gaussians(MoG), Non-maximum Suppression(NMS), HSV,
  HoG(Histogram of Gaussians), SIFT.
  \newline
  \newline
\end{list3}
\vspace{2mm}
\section{Other Projects} \\
{$\ $} \vspace{-2mm} \\
\begin{twentyshort} % Environment for a short list with no descriptions
  \twentyitemshort{\sbt  ScalaComplier}{\qquad Scala compiler in Python,
    implements dynamic}
  \vspace{1mm}
  \twentyitemshort{\faGithub
    \href{http://www.github.com/Nishant9/scalaCompiler}{\texttt{Nishant9/scalaCompiler}}}{\qquad
    scoping, type checking and basic type inference.}

  \twentyitemshort{\sbt  CodeCloud}{\qquad Code management website primarily for
    Competitve}
  \vspace{1mm}
  \twentyitemshort{\faGithub
    \href{http://www.github.com/Nishant9/ccloud}{\texttt{Nishant9/ccloud}}}{\qquad
    programming; uses django, bootstrap3 and sqlite}
  
  \twentyitemshort{\sbt  Operating Systems}{\qquad System calls,
    Signal handling, process scheduling}
  \vspace{1mm}
  \twentyitemshort{\faicon{bitbucket}\href{https://bitbucket.org/Nishant9/}{\texttt{Nishant9/CS330*}}}{\qquad and
    synchronization primitive for NachOS}
  \vspace{1mm}
  \twentyitemshort{\sbt  Web Platform}{\qquad Various features for a academic
    networking platform} 
  \vspace{1mm}
  \twentyitemshort{\sbt  Image Triangulation}{\qquad Image filter that renders image
    using only triangles}
  
  \twentyitemshort{\sbt  News Map}{\qquad Webapp that scrapes news websites, parses
    news }
  \twentyitemshort{}{\qquad for location and plots it on a map}
  \vspace{-0.4cm}   
	% \twentyitemshort{<dates>}{<title/description>}
\end{twentyshort}
\vspace{-3mm}

\end{document} 
